Multi-resolution Neural Field Estimation

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
correction to  EM equations
defined new indexing for  EM equations

where $[.]_{i,j}$ denotes $\left(i,j\right)$-element of the matrix, and $ [.]^{i,j}$ denotes $\left(i,j\right)$-block of the  block matrix and where

@@

[\Gamma_3]^{j,i}&=\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{i,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,j}\label{eq:Gamma3}.

@@

where $[.]_{j:} $ denotes $j^{th}$ row of the matrix. All blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed as a once-off before the commencement of the EM iterations. Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation

>>>>

where $[.]_{p,q}$ denotes $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes $\left(p,q\right)$-block of the block matrix and where

@@

[\Gamma_3]^{j,i}&=\sum_{k,m=1}^{n_x}[\mathbf{U}^{\top}]^{j,m}[ \boldsymbol\Lambda_{x}^{-1}\boldsymbol\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}]_{m,k}[\mathbf{U}]^{k,i}\label{eq:Gamma3}.

@@

where $[.]_{p:} $ denotes $p^{th}$ row of the matrix. All blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed as a once-off before the commencement of the EM iterations. Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation
